CLT Results

### 2022-04-11 analysis/clt_irt_analysis.Rmd
model run on cluster

# plot chart
ggplot(format, aes(Theta, P.1, col = aoa_german_comb, group = item)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  facet_wrap(~targetWord)+
  ylim(0,1)+
  scale_color_viridis_c(name = "AoA") +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```

>>>>

# plot chart
ggplot(format, aes(Theta, P.1, col = aoa_german_comb, group = item)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  #facet_wrap(~targetWord)+
  ylim(0,1)+
  scale_color_viridis_c(name = "AoA") +
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```
